\begin{thebibliography}{99}

\bibitem{RMWDeptAirLetter}
	Letter to WM Wilson from the Department of Air, 18 September 1953.
	\url{https://www.flickr.com/photos/freosam/14993078453} retrieved 24 October 2014.

\bibitem{HMHbirth}
	Western Australian registry of Births, 1915. Registration number 39 in the district of Sussex.

\bibitem{FBHguildford}
	Accomplished Old Guildfordians, 9 March 2012.
	\url{http://www.oldguildfordians.com.au/documents/accomplished/Accomplished_Old_Guildfordians.pdf}

\bibitem{FBHwar}
	SP196/3, H14: Captain Bertram Frank Hussey [24 pages] [Box 2], in National Archives of Australia, 1927--1939.
    \url{http://recordsearch.naa.gov.au/SearchNRetrieve/Interface/DetailsReports/ItemDetail.aspx?Barcode=3224471}

\bibitem{BMD}
	WA Registry of Births, Deaths and Marriages, reg. no. 637, 1888.

\bibitem{FamilyNotices}
	Family Notices. \emph{The West Australian} 11 April 1888, p. 2. Retrieved 4 November 2014,
	from \url{http://nla.gov.au/nla.news-article3117791}.

\bibitem{HMWnote}
	H. M. Wilson, date unknown. \emph{Children of George Walpole Leake and Rose Ellen}.
	\url{https://archive.org/details/ChildrenOfGeorgeWalpoleLeakeAndRoseEllen}

% Sarah Constance Lodge advertising for a general servant just prior to the birth of Helen Rose Lodge:
\bibitem{ServantAd}
	Classified Advertising. \emph{The West Australian} 15 March 1888, p. 3.
	Retrieved 4 November 2014 from \url{http://nla.gov.au/nla.news-article3117302}.

\bibitem{HAHandDarky}
	Harold Aubrey Hall and 'Darky', c.\ 1950s.
	\url{http://photos.samwilson.id.au/picture/1492}

\bibitem{SCLdeathNotice}
	Family Notices. \emph{The West Australian} 16 May 1939, p. 1. Retrieved November 16, 2014, from \url{http://nla.gov.au/nla.news-article46390957}.

\bibitem{WABMD208}
	Registry of Births, Deaths, and Marriages. Registration number 208 in the district of Claremont.

\bibitem{NAAA9300}
	From NAA series \#A9300: ``WILSON WILLIAM MURRAY : Service Number - 406376 : Date of birth - 04 Jun 1914 : Place of birth - CLAREMONT WA : Place of enlistment - PERTH WA : Next of Kin - WILSON HELEN Deceased.''

\bibitem{CompanyChiefs}
	 COMPANY CHIEFS MURDERED IN W.A. \emph{The Mercury} p.\ 2, 29 September 1953. Hobart, Tasmania.
	 \url{http://nla.gov.au/nla.news-article27174075}
	 ``A propelling pencil carried by one of the men was cut in two by a bullet before it entered his body.''

\bibitem{WADeaths}
	Index to general register of deaths Western Australia/Registrar General. [Perth, W.A.: Government Printer, 1967-198-.] Prepared in accordance with the requirements of section 17 of the Registration of Births, Deaths and Marriages Act, 1984-1956. 1841-1896, 1897-1905, 1906-1980 Microfiche Drawer no. 42; Call no. mc N 651 in the Newspapers/Microforms Reading room at the National Library of Australia.

\bibitem{WestAusDeathNotices}
	Index to death notices in the West Australian/ Western Australian Genealogical Society. [Bayswater, W.A.]: The Society, [1989]. 1985-1989, 1990-1992, 1993-1994, 1997-1998. Microfiche Drawer no. 44; Call no. mc N 486 in the Newspapers/Microforms Reading room at the National Library of Australia.

\bibitem{VictimEstate}
	\emph{Rifle Victim Left Estate Of \pounds 4,587} November 1953, The West Australian.
	\url{http://nla.gov.au/nla.news-article52943092}

\bibitem{InsanityVerdict}
	Verdict Of Insanity At Murder Trial. Sydney Morning Herald, 15 December 1953, p.\ 8.
	\url{http://nla.gov.au/nla.news-article18401354}

\bibitem{GuiltyInsane}
	Found Guilty But Insane. Townsville Daily Bulletin, 16 December 1953, p.\ 1.
	\url{http://nla.gov.au/nla.news-article63215264}

\bibitem{TimberDirectors}
	 2 TIMBER DIRECTORS KILLED IN WA OFFICE. \emph{Barrier Miner}, Broken Hill, NSW. 29 September 1953, p.\ 2.
	 \url{http://nla.gov.au/nla.news-article50066887}

\bibitem{MurderDirectors}
	Murder of Timber Directors. \emph{Barrier Miner} Broken Hill, NSW. 30 September 1953, p.\ 3.
	\url{http://nla.gov.au/nla.news-article50067079}

\bibitem{NewAngle}
	New Angle In W.A. Murders. \emph{The Advertiser}, Adelaide, SA. 30 September 1953, p.\ 3.
	\url{http://nla.gov.au/nla.news-article48928021}

\bibitem{DoubleMurder}
	Double Murder Charge Remand, \emph{Sunday Times} (Perth), p25, 18 October 1953.
	\url{http://nla.gov.au/nla.news-article59680487}

\bibitem{FawcettRemanded}
	FAWCETT IS AGAIN REMANDED. \emph{Mirror} (Perth, WA) 17 October 1953 p.\ 1.
	\url{http://nla.gov.au/nla.news-article75787673}

\end{thebibliography}
