\biohead{James Herbert Wilson}{}


%|death_date=1 June 1942
%|death_place=Perth, Western Australia
%|parents=[[Mary McHarg]]
%|partners=[[Edith Olive Hall]]

James Herbert Wilson (known as `Jim' to everyone save his mother; she called him Herbert) was born on 6 February 1872 in Collingwood, Melbourne<ref>{{cite |title=Victorian Pioneers Index on CD-ROM (1836-1888) |publisher=Registry of Births, Deaths and Marriages |location=Melbourne |accessdate=9 August 2014}} Registration number: 1823.</ref><ref name="vpi">Victorian Pioneers Index 1837–1888, National Library of Australia.  Birth certificate number 1823.  [Accessed 2007-20-10, [[user:samwilson]].]</ref> to \bioref{Mary_McHarg} and \bioref{}.

The family had land in Kinglake in Murrindindi Shire<ref>'[http://services.land.vic.gov.au/vicnames/ VICNAMES' online geographical name database]. [Accessed 2007-10-20, [[user:samwilson]]]</ref>, and in his early 20s Jim went there to grow potatoes so that he could earn some money to support the family<ref name="rae1">Hussey, R. c.1990, \url{http://hmwilson.archives.org.au/Rae\%27s_documents/JAMES_HERBERT_WILSON.doc} unpublished manuscript, held in the  H. M. Wilson Archives.</ref> back in Melbourne. While he was living up there in the little shack he built himself, his younger sister Jessie died of TB, and his brother \bioref{Oswald_Andrew_Wilson} moved to Perth to practise Architecture.\cite{rae1}.

* At the peak of the gold rush, c.~1890--95, Jim followed him and they went to find gold in Kalgoorlie, but with no luck\cite{rae1}.
* "He married in I think 1903 [actually 1904<ref name="vpi" />], living in a rented home in Lyall Street in South Perth".\cite{rae1}. Married [[Edith Olive Hall]] in 1904 in Perth<ref>Western Australian Department of Justice Online Index of Births, Deaths and Marriages 1841–1931. [accessed 2007-10-20 by [[user:samwilson]]].  Marriage registration number 1195.</ref>
*"and then I think after Jean and Gordon were born, he had a stroke of luck and won 100 pounds, whether on a horse or a lottery or a raffle I have no idea, but the result was that he was the owner of two blocks of land west of Subiaco. Andrew designed and supervised the building of the house."<ref name="rae1" />
* "In the middle of June of 1914 my father bought as farm at Quairading for which he paid 1000 pounds sterling.''\cite{rae2}<ref name="rae2">Hussey, R. c.1990.  [\url{http://hmwilson.archives.org.au/Rae\%27s_documents/James_Herbert_Wilson_continued.doc} Unpublished manuscript] held in the H. M. Wilson Archives.</ref> Avon Location 8286. Train to Perth.
* c.1920: pressure from family to sell farm (for £2000) as Charlie had started [[C. M. Wilson Pty. Ltd.]] in Murray Street<ref name="rae2"/>.
* Had a house in Shenton Park on half an acre. It's still there, although unrecognisable.<ref>Pers. comm. between R. Wilson and [[user:samwilson]], c.2005.</ref>
* Mid-thirties had a heart attach on the boat home from Devonport, got home and Charlie insisted he stop work<ref name="rae2"/>.
* Died 1942 in Perth.\cite{rae2}.
