\biohead{Millicent Joyce Branson Clifton}{}

Millicent Clifton was born in 1912 in Plantagenet\cite{MJBCbirth} to Joy and \bioref{Gervase_Clifton}, and died suddenly at only 8 years old in Perth in 1920.\cite{MJBCdeath}

The following obituary was published in \emph{The Daily News} on October 28:\cite{MJBCobit}

\begin{quotation}
\begin{center}
OBITUARY \\
THE LATE MISS MILLICENT CLIFTON.
\end{center}

The funeral of the late Miss Millicent Joyce Branson Clifton, youngest daughter of Mr. Gervase Clifton (Curator of Intestate Estates), and Mrs Clifton, of 51 Newcastle-street, Perth, took place on Tuesday afternoon. The cortege moved from their residence, 51 Newcastle-street, Perth, and proceeded by road to the Anglican portion of the Karrakatta Cemetery, where the remains were laid to rest. The Rev.\ Minor Canon W. Patrick conducted the burial service. The chief mourners were:---Mr. and Mrs. G. Clifton (parents), Miss Tita Clifton, Miss Lily Clifton, and Miss Lulu Clifton (sisters), Messrs. R. C. Clifton, G. A. Clifton, Robert Clifton, Gervase Clifton, jun. (relatives). The pall-bearers were:---Messrs. E. H. Barker, A. Halliday, R. Rolland, and R. H. Downes. Among those present were:---Messrs. M. M. Moss, H. S. Crofts, A. Crassweller, F. Elliott, C. F. Bayliss, T. Hawley, J. Robson, J. Farley, and Edmondson, Mrs. Warburton, Miss Warburton. Miss Brenton Coward, Miss. Cadman, Miss Marshall. Wreaths were sent by officers Curator of In testate Estates' office, North Perth Cricket Club, Matron and Staff Children's Hospital, Roseworthy School, Mr. M, M. Moss, the Principals Roseworthy School (Misses Coward, Cadman and Marshall), Mrs. G. E. Warburton, and Miss Warburton, Mr. and Mrs. Alex. Halliday, Messrs. Suton, Newman, and Eastwood, Mrs. Purser and Ngaerary, Mrs. Cooper, Mollie Rolland, Mr. and Mrs. Ed. Barber, Mrs. Columbus and family. Battyes and Fordhams, Violet Bethell, Edith Tothill, Nurse Phillips, Mrs. Devenish, Miss Jecks, Alex. Dargie, Ngaere Purser, Daddy and Mummie, Loulou and Cubby, Aunt Nellie, Aunt Emma and family, Tita and Lily, and many others. Numerous telegrams, letters and messages of sympathy and condolence were received by the family in their sad and sudden bereavement. The funeral arrangements were carried out by Messrs. C. H. Smith and Co.
\end{quotation}
