\biohead{Sarah Constance Leake}{Sarah_Constance_Leake}{}

Date of Death 	May 15th, 1939
Mother 	Rose Ellen Leake
Father 	George Walpole Leake
Siblings 	Blanche Kelsall, Jane Adam, Jessie Skinner, Lady Parker, Mary Parry, Rose Clifton.
Children 	Helen Rose Hall, 1 son, 1 other daughter

Sarah Constance Lodge (n\'{e}e Leake) was born on 1 February 1860. She married Thomas Soutter Lodge (\p{Thomas_Soutter_Lodge}) on the 15\textsuperscript{th} of September 1886 (her granddaughter Helen Margaret Wilson (\p{Helen_Margaret_Hall}) married her first husband Peter James Donegan exactly fifty years later, to the day\cite{HMWnote}).

% Sarah Constance Lodge advertising for a general servant just prior to the birth of Helen Rose Lodge:
Lived in Grass Valley, near Northam.\cite{ServantAd}

Advertised for a general servant three weeks before the birth of their daughter Constance (\p{Helen_Rose_Lodge}) in 1888.\cite{ServantAd}

Two other children: Joan and Jack.\cite{SCLdeathNotice}

Known as Constance (and `Gag' by her grandchildren).

The notice of her death, published in the West Australian, was as follows:\cite{SCLdeathNotice}

\begin{quotation}
LODGE.---On May 15, 1939, at her residence, 130 Broome-street, Cottesloe, Sarah Constance, beloved wife of the late Thomas Soutter Lodge, late of Strelly, Busselton, and loving mother of Helen (Mrs. Aubrey Hall, Carnarvon), Joan (Mrs. Norman Martin, Cottesloe), and Jack (Capel); forth daughter of the late George Walpole Leake, Q.C.; aged 79 years.
\end{quotation}
