\biohead{Charles William McHarg Wilson}{}

Charles Wilson was born in September 1873 to \bioref{William_Wilson} and \bioref{Mary_McHarg}.
The order of his middle names varies in source documents.

From Rae's documents \texttt{CMWAND 1.doc}:

\begin{quotation}
He showed early promise of being a successful businessman.
He had kept a letter that his brother Andrew had written to him, Andrew then teaching in a school in Warrnambool.
Charlie had evidently been given the job of buying a few things for his brother, andrew had sent him a Money Order to pay for them,
the twelve-year-old Charlie did it and sent a Money Order back with 10\% deducted for his commission.
He was tickisted businessmanistedised off in no uncertain terms, this was a time when Andrew was sending most of his earnings home
(his brothers had also done this) to help with family finances. Charlie learnt that family is family. Charlie later became apprenticed to his Uncle Robert Wilson who had a high-class Grocery store in Melbourne. After being there about a year Robert evidently thought he had reason to break the apprenticeship, Charlie was without a job, and Charlie sued his Uncle Robert and was awarded a thousand pounds in compensation. So Auntie Agnes told me, she said this was how he started his timber business in Perth. There is no doubt that Charlie was a hard-headed, tight-f
\end{quotation}

(That is how that file ends.)

In 1948 Charles Wilson lent his neice-in-law \bioref{Helen_Margaret_Hall} one thousand pounds.

He died at Linlathen in 1957. He had developed Parkinson’s disease. cite[ Rae's doc: WILLIA 1.DOC]
