\biohead{Dennis Lodge Martin}{c.1942, possibly in Darwin.}
\index{Martin, Dennis lodge}

The following is the biography presented by the family on 23 May 2009 when a Kings Park plaque was dedicated in Dennis' memory:\cite{KingsParkDennisMartin}

\begin{quotation}
Flight Sergeant Dennis Lodge Martin of 21 Squadron was born in Perth in October 1916 to Norman and Joan Martin of Cottesloe.

He and his older brother, Warrant Officer (Class 2) Frederick Martin, attended Scotch College,
played rugby with Cottesloe Club and were members of the Cottesloe Surf Life Saving Club.
They had two sisters---Jan and Pat (and Pat married Sergeant John Walrond).

After leaving college, Dennis worked as a shearer and farm hand and was married to Sylvia.
He was the only family member with a car, which he called 'Pansey'.

Dennis enlisted in the RAAF in February 1940 and was posted to 21 Squadron at Laverton.
The squadron, flying Buffaloes, was located in Malaya until they were evacuated to Australia.

They were then equipped with Vengeance aircraft. In July 1944 the squadron was equipped with Liberator heavy bombers
to carry out raids on Japanese convoys and reconnaissance duties.

Flight Sergeant Dennis Lodge Martin, service number 8811 of 21 Squadron, was killed in action when Liberator number A72-61,
on which he was the flight engineer, was shot down near Balikpapan, Borneo on 1 July 1945. He was 28 years of age.
\end{quotation}

Two death notices, Family Notices (1945, July 27). The West Australian (Perth, WA), p. 1.
Retrieved April 11, 2020, from http://nla.gov.au/nla.news-article51760309

"MARTIN (Dennis Lodge). F/Sgt RAAF (E), killed In air operatIons, Balik Papan.
July 1, 1945; beloved husband of Sylvia and only surviving son of Mr
and Mrs Norman Martin (128 Broome-street, Cottesloe); brother of Fred (AIF.
killed in Syria), Pat Walrond and Janet; brother-in-law of John (AIF,. killed in NG)."

"MARTIN (Dennis Lodte), F/Sgt, RAAF (E), loved son-in-law of Mr and Mrs J. Tivey, and brother-in-law of Bill (Burns-street, Maidstone, Victoria)."
