\biohead{Helen Margaret Hall}{}\index{Hall, Helen Margaret}\index{Wilson, Helen Margaret}\index{Donegan, Helen Margaret}\index{Marnie}

Helen Margaret Hall was born at Nurse Killerby's Hospital in \idx{Busselton}, Western Australia\cite{HMHbirthNotice}
on 10 July 1915.\cite{HMHbirth}
Her parents (\bioref{Harold_Aubrey_Hall} and \bioref{Helen_Rose_Lodge}) were living there at the time.

She married \bioref{Peter_Innes_Donegan} on 15 September 1936 in St~Georges Cathedral in \idx{Perth}.\cite{MargPeterMarriage}
Aubrey wasn't there, so Margaret's mother's brother \bioref{Robert_John_Lodge} gave her away.\cite{DoneganHallWedding1936}con

The West Australian published the following on 23 September:\cite{DoneganHallWedding1936}

\begin{quotation}
Donegan---Hall

Wedding.

\textsc{The} marriage was solemnised on Tuesday evening, September 15, at St.\ Mary's Church, Colin-street, West Perth,
between Mr.\ Peter Donegan, son of Mr.\ and Mrs.\ Ernest Donegan, of Subiaco, and Miss Margaret Hall, daughter of Mr.\
and Mrs.\ Aubrey Hall, of Carnarvon. The Rev.\ F.\ Stillwell performed the ceremony. The date chosen for the wedding
also marked the celebration of the golden wedding of the bride's grandparents, Mr.\ and Mrs. T.S.\ Lodge, of
Broome-street, Cottesloe.

In the absence of her father the bride was given away by her uncle, Mr.\ Jack Lodge, and wore a charming trained frock of
white lace, cut on gracefully simple lines. Her filmy tulle veil (which had been worn by her mother on her wedding day)
was held in place with a halo of silver lame and orange blossom, and she carried a beautiful bouquet of white plum blossom and clematis.

There were three bridesmaids, Misses Patricia and Judith Donegan, and Joan Hall Miss Patricia Donegan wore a graceful cape frock of pale coral pink
georgette and carried a posey of pink and mauve flowers. Misses Judith Donegan and Joan Hall wore frocks of mauve
georgette relieved with deep violet, and carried posies of violets.
Mr.\ Tom Draper was best man and Messrs.\ G.\ McCausland and F.\ Martin were groomsmen.

After the ceremony a small reception was held at 8 Outram-street, West Perth, the home of Mrs. Ernest Hall,
who wore a deep blue lace frock. Mrs. A. Hall (mother of the bride) chose a frock of navy blue floral georgette and carried
a bouquet of crimson sweet peas. Mrs. Ernest Donegan (mother of the bride groom) wore a saxe blue frock with a matching coat of blue velvet.
Special guests at the reception were Mr. and Mrs. T. S. Lodge (the grandparents of the bride) whose toasts were honoured
with those of the bride and bridegroom. Later in the evening the bride and bridegroom left by motor car for their honeymoon,
the bride travelling in a smart ensemble in two shades of blue.
\end{quotation}

They had one daughter, in 1938.\cite{JHBirthNotice}
Peter died in 1939 in an aviation accident.

She remarried on 2 July 1941\cite{MurrayMargMarriageNotice} to \bioref{William_Murray_Wilson}
(also in St~George's Cathedral\cite{MurrayMargMarriageNotice}), with whom she had two sons.

Lived at 8 Outram Street in West Perth for nine years (including WW2) with Judy.\cite{OutramStPhoto}
She rented the house from her father's cousin Ernest Hall.

She died on 21 February 2000 in East \idx{Fremantle}, Western Australia, at the Braemar nursing home,
and her ashes were interred in Murray's grave at Karrakatta.
