\biohead{James Herbert Wilson}{}
\index{Wilson, James Herbert}
\index{Jim Wilson}

James Herbert Wilson (known as `Jim' to everyone save his mother; she called him Herbert) was born on 6 February 1872 in Collingwood, Melbourne\cite{VicPioneers} to \bioref{Mary_McHarg} and \bioref{William_Wilson}.

The family had land in Kinglake in Murrindindi Shire,\cite{VicNames} and in his early 20s Jim went there to grow potatoes so that he could earn some money to support the family\cite{rae1} back in Melbourne.
While he was living up there in a small shack he built himself, his younger sister Jessie died of TB,
and his brother \bioref{Oswald_Andrew_Wilson} moved to Perth to practise Architecture.\cite{rae1}.

At the peak of the gold rush, c.~1890--95, Jim followed him and they went to find gold in Kalgoorlie, but with no luck\cite{rae1}.

He married \bioref{Edith_Olive_Hall} in 1904 in Perth\cite{JimEdithMarriage},
when they were living in a rented house in Lyall Street in South Perth.\cite{rae1}

"and then I think after Jean and Gordon were born, he had a stroke of luck and won 100 pounds, whether on a horse or a lottery or a raffle I have no idea, but the result was that he was the owner of two blocks of land west of Subiaco. Andrew designed and supervised the building of the house."\cite{rae1}

"In the middle of June of 1914 my father bought as farm at Quairading for which he paid 1000 pounds sterling.''\cite{rae2}
Avon Location 8286. Train to Perth.

c.1920: pressure from family to sell farm (for £2000) as Charlie had started [[C. M. Wilson Pty. Ltd.]] in Murray Street.\cite{rae2}

Had a house in Shenton Park on half an acre. It's still there, although unrecognisable.

Mid-thirties had a heart attach on the boat home from Devonport, got home and Charlie insisted he stop work.\cite{rae2}

Jim died on 1 June 1942 in Perth.\cite{rae2}
