\biohead{Olive Adele Wilson}{}

Adele was born in 1908 to \bioref{James_Herbert_Wilson} and \bioref{Edith_Olive_Hall},
and grew up in Lyall Street in South Perth.\cite{rae1}

She married \bioref{James_William_Lang} in 1936.
Their wedding was reported in \emph{The West Australian} as follows:\ref{WestAust1936}

\begin{quotation}
Lang—Wilson Wedding.

\textsc{The} marriage was solemnised in the \idx{Ross Memorial Church}, on Tuesday evening, April 21, between Miss Adele Wilson,
second daughter of Mr. and Mrs. J. H. Wilson, of Shenton Park, and Mr. James Lang, elder son of Mr. and Mrs. J. W. Lang,
of Salisbury-street, Subiaco. Dr. Munro Ford officiated. The bride, who was given away by her father,
wore a frock of parchment satin, the cowled bodice falling Into soft folds and the draped sleeves finished with small buttons
to the elbow. The simply cut skirt fell into a long train. Her veil delicately embroidered with acorns fell from a
coronet of orange blossom, and she carried a trailing bouquet of white and pink flowers.

There were two bridesmaids, Misses Rae Wilson (sister of the bride) and Jenny Lang (sister of tbe bridegroom).
Both wore frocks of pale green georgette, the pleated bodices embroidered in silver thread on neck and sleeves.
Their hats of stiffened green tulle were finished at the back with green velvet flowers,
and they carried trailing bouquets of pale pink rosebuds.
Mr. J. Abrahams was best man, and Mr. Murray Wilson groomsman.

After the ceremony, Mr. and Mrs. Wilson held a reception at the Karrakatta Club hall.
They were assisted by Mr. and Mrs. J. W. Lang in receiving the guests.
Mrs. Wilson wore a frock of deep lido blue lace with a velvet coat in the same shade and a smart velour hat to match and carried a bouquet of red roses.
Mrs. Lang's frock was of black velvet with touches of gold and she wore a becoming hat of black velour and carried a bouquet of gold roses.
Dr. Munro Ford presided at the wedding breakfast and the usual toasts were honoured.
During the evening the bride and bridegroom left for their honeymoon, the bride travelling in a smart brown crepe ensemble in military style,
with stone-marten furs. Mr. and Mrs. Lang will make their future home at Nedlands.
\end{quotation}
