\begin{thebibliography}{999}
\footnotesize

\bibitem{BruceWilsonBirth}
    Western Australian Registry of Births (1918). Perth district, number 2646, Herbert Bruce Wilson.

\bibitem{WelcomeWalls}
	Western Australian Museum \emph{Welcome Walls}, panel 329.
	\url{http://www.museum.wa.gov.au/welcomewalls/names/hall-henry-sarah-family}

\bibitem{JLHbirth}
	Family Notices (1919, November 5). The West Australian, p. 1.
	Retrieved October 23, 2016, from \url{http://nla.gov.au/nla.news-article27666905}.
	``HALL.---On August 24, at Roebourne, to Mr. and Mrs. Aubrey Hall---a daughter (Joan Leake).''

\bibitem{Connie1983}
	Autobiography by C. B. Berryman, 1983.
	\url{https://archive.org/details/C.B.Berryman1983}

\bibitem{Connie1983OralHistory}
	Oral history interview with Constance Berryman, 1983.
	\url{https://archive.org/details/SLWA_b1794680/}

\bibitem{OutramStPhoto}
	Photo of 8 Outram Street with inscription by Margaret Wilson.
	\url{https://hmwilson.archives.org.au/items/99.html}

\bibitem{Connie1966}
	Handwritten account of the family history of C.B. Berryman (n\'{e}e Hall). 1966.
	\url{https://archive.org/details/ConstanceBoydBerrymanFamilyHistory}

\bibitem{KC00051342}
	Metropolitan Cemeteries Board, Summary Of Record Information. KC00051342.
	Aged 66, died 04/06/1976. Suburb: Como.
	Grave location: Anglican XC 180.
	\url{https://www2.mcb.wa.gov.au/NameSearch/details.php?id=KC00051342}

\bibitem{HAHmarriage}
	Index to Western Australian births, deaths and marriages.
	Registration \#14 in Sussex district. 1910.

\bibitem{HallLodgeWedding}
	\emph{Family Notices} (1910, December 8). The West Australian (Perth, WA: 1879--1954), p.\ 1.
	\url{https://hmwilson.archives.org.au/items/114.html}
	\url{http://nla.gov.au/nla.news-article26297910}

\bibitem{VicPioneers}
	Victorian Pioneers Index 1837--1888, National Library of Australia.
	Birth certificate number 1823.

\bibitem{VicNames}
	VICNAMES online geographical name database.
	\url{http://services.land.vic.gov.au/vicnames/}

\bibitem{JimEdithMarriage}
	Western Australian Department of Justice Online Index of Births, Deaths and Marriages 1841–1931.
	Perth. Marriage registration number 1195.

\bibitem{JimEdithMarriageCert}
	Certificate of marriage of James Herbert Wilson and Edith Olive Hall, 1904.
	Via Ancestry user Jennibarryb.
	\url{https://archive.org/details/JamesEdithWilsonMarriageCert1904}

\bibitem{rae2}
	Hussey, R. c.1990.
	\url{http://hmwilson.archives.org.au/Rae\%27s_documents/James_Herbert_Wilson_continued.doc}
	Unpublished manuscript held in the H. M. Wilson Archives.

\bibitem{WestAusSocialNotes1913}
	``SOCIAL NOTES.'' \emph{The West Australian}, 24 Jul 1913: p.\ 8.
	\url{http://nla.gov.au/nla.news-article26880452}

\bibitem{LondonGazette1945}
	\emph{Supplement to The London Gazette}, 21 August 1945, p.\ 4220.
	\url{https://www.thegazette.co.uk/London/issue/37232/page/4220/data.pdf}

\bibitem{GilmoreEngagement1944}
	\emph{What Women Are Doing.} (1944, September 14). The West Australian, p. 3.
	Retrieved October 21, 2015, from \url{http://nla.gov.au/nla.news-article44977997}.

\bibitem{AOWisonBio}
	\emph{Andrew Oswald Wilson} by Dr John J. Taylor, July 2013.
	\url{http://www.architecture.com.au/docs/default-source/wa-notable-buildings/wilson-andrew-oswald.pdf}
	archived at \url{http://www.webcitation.org/6b2A9WkrZ}

\bibitem{Argus1866Aug28}
	Family Notices. (1866, August 27). The Argus (Melbourne, Victoria: 1848--1957), p. 4.
	Retrieved August 25, 2015, from \url{http://nla.gov.au/nla.news-article5771652}.
	``WILSON.---On the 16th inst., at her residence, Victoria-parade, Mrs William Wilson of a son.''

\bibitem{MaryMcHargMarriage}
	Marriage certificate of Mary McHarg and William Wilson, Victoria. 1864, registration number 2013.

\bibitem{MJBCbirth}
	WA BMD Register. 1912. Plantagenet district, registration number 203.

\bibitem{MJBCdeath}
	WA BMD Register. 1920.
	``CLIFTON, MILLICENT J B, Female, PERTH, reg.\ 1399.''

\bibitem{CaptainHusseyDisplay}
	Information display about Frank Hussey at the Settlement railway station, Rottnest.
	\url{https://flic.kr/p/tDFQtA}

\bibitem{CaptainHusseyPhoto}
	Photo of \emph{Captain Hussey}. \url{https://flic.kr/p/tTWyH1}

\bibitem{MJBCobit}
	Family Notices. (1920, October 28). The Daily News (Perth, WA: 1882--1950), p. 3 3rd edition.
	Retrieved November 24, 2014, from \url{http://nla.gov.au/nla.news-article79564663}

\bibitem{HBLMarriageNotice}
	Marriages and Deaths. Marriages. (1868, November 11).
	\emph{The Inquirer and Commercial News} (Perth, WA: 1855--1901), p. 2.
	Retrieved November 19, 2014, from \url{http://nla.gov.au/nla.news-article69384582}

\bibitem{ErnestHallInscription}
	Inscription on the reverse of a cut photo of Ernest Hall. Date unknown.
	\url{https://hmwilson.archives.org.au/items/155.html}

\bibitem{ErnestAubreyHannah}
	Ernest and Aubrey with their mother Hannah Hall, in Cossack.
	\url{https://hmwilson.archives.org.au/items/152.html}

\bibitem{ConnieBirthNotice}
	Family Notices. (1912, September 3). \emph{The West Australian} (Perth, WA: 1879--1954), p. 1.
	Retrieved November 18, 2014, from \url{http://nla.gov.au/nla.news-article26520217}
	``BIRTHS. \dots HALL.---On August 9, at their residence, Roebourne to Mr. and Mrs. Aubrey Hall---a daughter.''

\bibitem{ConnieWedding}
	Wedding Bells. (1937, May 26). \emph{Northern Times} (Carnarvon, WA: 1905--1952), p. 2.
	Retrieved November 18, 2014, from \url{http://nla.gov.au/nla.news-article75120076}

\bibitem{RMWDeptAirLetter}
	Letter to WM Wilson from the Department of Air, 18 September 1953.
	\url{https://www.flickr.com/photos/freosam/14993078453} retrieved 24 October 2014.

\bibitem{HMHbirth}
	Western Australian registry of Births, 1915. Registration number 39 in the district of Sussex.

\bibitem{HMHbirthNotice}
	Family Notices (1915, July 16). Western Mail (Perth, WA: 1885 - 1954), p. 23. Retrieved October 30, 2018, from \url{http://nla.gov.au/nla.news-article37428852}
	``HALL.---On July 10, at Nurse Killerby's Hospital, Busselton, to Mr. and Mrs. H. Aubrey Hall, of Cossack---a daughter.''

\bibitem{MargPeterMarriage}
	Western Australian registry of Marriages, 1936. Registration number 1472 in the district of Perth.

\bibitem{DoneganHallWedding1936}
	Donegan---Hall Wedding. (1936, September 23). The West Australian (Perth, WA: 1879--1954), p.\ 4.
	Retrieved May 8, 2019, from \url{http://nla.gov.au/nla.news-article40961560}

\bibitem{FBHguildford}
	Accomplished Old Guildfordians, 9 March 2012.
	\url{http://www.oldguildfordians.com.au/documents/accomplished/Accomplished_Old_Guildfordians.pdf}

\bibitem{FBHwar}
	SP196/3, H14: Captain Bertram Frank Hussey [24 pages] [Box 2], in National Archives of Australia, 1927--1939.
	\url{http://recordsearch.naa.gov.au/SearchNRetrieve/Interface/DetailsReports/ItemDetail.aspx?Barcode=3224471}

\bibitem{BMD}
	WA Registry of Births, Deaths and Marriages, reg. no. 637, 1888.

\bibitem{FamilyNotices}
	Family Notices. \emph{The West Australian} 11 April 1888, p. 2. Retrieved 4 November 2014,
	from \url{http://nla.gov.au/nla.news-article3117791}.

\bibitem{HMWnote}
	H. M. Wilson, date unknown. \emph{Children of George Walpole Leake and Rose Ellen}.
	\url{https://archive.org/details/ChildrenOfGeorgeWalpoleLeakeAndRoseEllen}

% Sarah Constance Lodge advertising for a general servant just prior to the birth of Helen Rose Lodge:
\bibitem{ServantAd}
	Classified Advertising. \emph{The West Australian} 15 March 1888, p. 3.
	Retrieved 4 November 2014 from \url{http://nla.gov.au/nla.news-article3117302}.

\bibitem{HAHandDarky}
	Harold Aubrey Hall and 'Darky', c.\ 1950s.
	\url{https://commons.wikimedia.org/wiki/File:Harold_Aubrey_Hall_riding.png}

\bibitem{SCLdeathNotice}
	Family Notices. \emph{The West Australian} 16 May 1939, p. 1. Retrieved November 16, 2014, from \url{http://nla.gov.au/nla.news-article46390957}.

\bibitem{WABMD208}
	Registry of Births, Deaths, and Marriages. Registration number 208 in the district of Claremont.

\bibitem{NAAA9300}
	From NAA series \#A9300: ``WILSON WILLIAM MURRAY: Service Number - 406376
	: Date of birth - 04 Jun 1914: Place of birth - CLAREMONT WA
	: Place of enlistment - PERTH WA: Next of Kin - WILSON HELEN Deceased.''

\bibitem{MurrayMargMarriageNotice}
    Family Notices (1941, July 5). The West Australian (Perth, WA), p. 1.
    Retrieved October 30, 2018, from \url{http://nla.gov.au/nla.news-article47151167}
    ``WILSON--DONEGAN.---On July 2. 1941 (by special licence), at St. George's Cathedral Perth, by the Rev. Dean Moore,
    William Murray (R.A.A.F.), second son of Mr. and Mrs. J. H. Wilson, of Shenton Park,
    to Helen Margaret, second daughter of Mr. and Mrs. H. Hall, of West Perth and Carnarvon.

\bibitem{CompanyChiefs}
	 COMPANY CHIEFS MURDERED IN W.A. \emph{The Mercury} p.\ 2, 29 September 1953. Hobart, Tasmania.
	 \url{http://nla.gov.au/nla.news-article27174075}
	 ``A propelling pencil carried by one of the men was cut in two by a bullet before it entered his body.''

\bibitem{WADeaths}
	Index to general register of deaths Western Australia/Registrar General. [Perth, W.A.: Government Printer, 1967-198-.] Prepared in accordance with the requirements of section 17 of the Registration of Births, Deaths and Marriages Act, 1984-1956. 1841-1896, 1897-1905, 1906-1980 Microfiche Drawer no. 42; Call no. mc N 651 in the Newspapers/Microforms Reading room at the National Library of Australia.

\bibitem{WestAusDeathNotices}
	Index to death notices in the West Australian/ Western Australian Genealogical Society. [Bayswater, W.A.]: The Society, [1989]. 1985-1989, 1990-1992, 1993-1994, 1997-1998. Microfiche Drawer no. 44; Call no. mc N 486 in the Newspapers/Microforms Reading room at the National Library of Australia.

\bibitem{VictimEstate}
	\emph{Rifle Victim Left Estate Of \pounds 4,587} November 1953, The West Australian.
	\url{http://nla.gov.au/nla.news-article52943092}

\bibitem{InsanityVerdict}
	Verdict Of Insanity At Murder Trial. Sydney Morning Herald, 15 December 1953, p.\ 8.
	\url{http://nla.gov.au/nla.news-article18401354}

\bibitem{GuiltyInsane}
	Found Guilty But Insane. Townsville Daily Bulletin, 16 December 1953, p.\ 1.
	\url{http://nla.gov.au/nla.news-article63215264}

\bibitem{TimberDirectors}
	 2 TIMBER DIRECTORS KILLED IN WA OFFICE. \emph{Barrier Miner}, Broken Hill, NSW. 29 September 1953, p.\ 2.
	 \url{http://nla.gov.au/nla.news-article50066887}

\bibitem{TheAge1935}
	Directors Shot Dead in W.A. (1953, September 29). The Age (Melbourne, Vic.: 1854--1954), p. 3.
	Retrieved August 13, 2020, from \url{http://nla.gov.au/nla.news-article206461419}

\bibitem{HEHDeathNotice}
	Family Notices (1941, June 10). \emph{The West Australian}, p. 1.
	Retrieved November 25, 2017, from \url{http://nla.gov.au/nla.news-article47147242}

\bibitem{Lepers1926}
	Lepers in the Nor-West (1926, August 29). ''Sunday Times', p. 11 (Second Section).
	Retrieved November 25, 2017, from \url{http://nla.gov.au/nla.news-article58248168}

\bibitem{MurderDirectors}
	Murder of Timber Directors. \emph{Barrier Miner} Broken Hill, NSW. 30 September 1953, p.\ 3.
	\url{http://nla.gov.au/nla.news-article50067079}

\bibitem{NewAngle}
	New Angle In W.A. Murders. \emph{The Advertiser}, Adelaide, SA. 30 September 1953, p.\ 3.
	\url{http://nla.gov.au/nla.news-article48928021}

\bibitem{DoubleMurder}
	Double Murder Charge Remand, \emph{Sunday Times} (Perth), p25, 18 October 1953.
	\url{http://nla.gov.au/nla.news-article59680487}

\bibitem{FawcettRemanded}
	FAWCETT IS AGAIN REMANDED. \emph{Mirror} (Perth, WA) 17 October 1953 p.\ 1.
	\url{http://nla.gov.au/nla.news-article75787673}

\bibitem{SouthWestNews1913}
	1913 `Family Notices.' The South-Western News, 2 May 1913, p.~3,
	retrieved 3 February 2015 from \url{http://nla.gov.au/nla.news-article147529167}

\bibitem{SMHDoubleMurder}
	\emph{Double Murder Charge In W.A.}, The Sydney Morning Herald. 30 September 1953 p.~6
	\url{http://nla.gov.au/nla.news-article18379987}
	``He stood silently at attention during the proceedings, which lasted little more than 30 seconds.
	He was not represented by counsel.''

\bibitem{JackLodgeBirthCert}
	Index to the WA Registry of Births, Deaths \& Marriages, Beverley district birth, reg.~no.~1789.

\bibitem{SouthWestern1918}
	PERSONAL. (1918, October 25). \emph{The South-Western News} (Busselton, WA), p. 3.
	Retrieved June 23, 2020, from \url{http://nla.gov.au/nla.news-article148130944}

\bibitem{PioneerFarmer1938}
	A Pioneer Farmer. (1938, March 1). \emph{The West Australian} (Perth, WA: 1879--1954), p.\ 3.
	Retrieved June 23, 2020, from \url{http://nla.gov.au/nla.news-article41663658}

\bibitem{RIA2004}
	Annual Report for the year ended 30 June 2004, Rottnest Island Authority.
	\url{http://www.rottnestisland.com/docs/ria-annual-report/annual_report_0304.pdf?Status=Master}
	\url{http://www.webcitation.org/6YFHlBal3}

\bibitem{rae1}
	Hussey, R. c.~1990, \url{http://hmwilson.archives.org.au/Rae\%27s_documents/JAMES_HERBERT_WILSON.doc}
	unpublished manuscript, held in the  H. M. Wilson Archives.

\bibitem{RaeWestAus}
	\emph{Fortress named a heritage icon}, 11 November 2010. Kent Acott.
	\url{https://au.news.yahoo.com/thewest/a/8298751/fortress-named-a-heritage-icon/}
	\url{http://www.webcitation.org/6YFHtUpaU}

\bibitem{WestAus1936p19}
	1936 `ISLAND WEDDINGS.', \emph{The West Australian} (Perth, WA: 1879--1954), 4 March, p.\ 19, viewed 3 May, 2015.
	\url{http://nla.gov.au/nla.news-article25131045}

\bibitem{WesternMail1936}
	No title. (1936, January 23). Western Mail (Perth, WA: 1885--1954), p. 31. Retrieved May 3, 2015,
	from \url{http://nla.gov.au/nla.news-article37778931}

\bibitem{WestAus1936p4}
	No title. (1936, March 4). The West Australian (Perth, WA: 1879 - 1954), p. 4.
	Retrieved May 3, 2015, from \url{http://nla.gov.au/nla.news-article25131060}

\bibitem{MilitaryWedding}
	Brilliant Military Wedding. (1936, March 8). Sunday Times (Perth, WA: 1902 - 1954), p. 24.
	Retrieved May 3, 2015, from \url{http://nla.gov.au/nla.news-article58764110}

\bibitem{AdaHallBabtism}
	``Australia Births and Baptisms, 1792--1981'', FamilySearch
	(\url{https://familysearch.org/ark:/61903/1:1:XTXQ-CYY} accessed 8 August 2015),
	Ada Maud Florence Hall, 26 May 1878; citing Roebourne, Western Australia, Australia;
	FHL microfilm 284,852.

\bibitem{rae1943}
    1943 Australian and American Nurses, Rae Hussey, New Guinea \url{https://w.wiki/6gS}
    ``Censorship pass expires 2.5.43. Passed by operational censor. Photo no. 14556.
    Issued by Department of Information, Commonwealth of Australia. Australian and American nurses in New Guinea:
    When Australian and Americans meet and chat by the side of a road somewhere in New Guinea. The group includes:---
    Miss N. Lanouette of Milford, New Hampshire, Sister R. Wilson of Perth, Western Australia,
    Miss Mary King of Stamps, Arkansas, Sister P. McDonald of Adelaide, South Australia,
    and Miss Helen Gray of Washington, D.C.''

\bibitem{JHBirthNotice}
    Family Notices (1938, March 15). The Advertiser (Adelaide, SA: 1931--1954), p. 14.
    Retrieved October 31, 2018, from \url{http://nla.gov.au/nla.news-article74218032}
    ``DONEGAN.---To Mr. and Mrs. Peter Donegan, Prospect---a daughter, at Berklea Hospital, Prospect.''

\bibitem{1904AubreyAgent}
    SHIPPING. (1904, March 5). The Pilbarra Goldfield News (Marble Bar, WA: 1897--1923), p. 1.
    Retrieved October 31, 2018, from \url{http://nla.gov.au/nla.news-article146130997}

\bibitem{CossackMayoralty}
	COSSACK. (1900, November 23). \emph{The Inquirer and Commercial News} (Perth, WA: 1855--1901), p. 11.
	Retrieved July 14, 2020, from \url{http://nla.gov.au/nla.news-article67065667}

\bibitem{NorthernTimes1912}
	Roebourne. (1912, April 27). Northern Times (Carnarvon, WA: 1905--1952), p. 4.
	Retrieved July 8, 2020, from \url{http://nla.gov.au/nla.news-article74893394}

\bibitem{NorthernTimes1933}
	A BUSH TRAGEDY. (1933, December 20). \emph{Northern Times} (Carnarvon, WA: 1905--1952), p. 5.
	Retrieved July 13, 2020, from \url{http://nla.gov.au/nla.news-article74871116}

\bibitem{ADBWSHall}
	H. Margaret Wilson, ``Hall, William Shakespeare (1825--1895)'',
	Australian Dictionary of Biography, National Centre of Biography, Australian National University,
	\url{http://adb.anu.edu.au/biography/hall-william-shakespeare-3697/text5789},
	published first in hardcopy 1972, accessed online 31 July 2019.

\bibitem{EADoneganGrave}
	Find-a-Grave record for grave of E.A. Donegan et. al.
	\url{https://www.findagrave.com/memorial/81687109/ernest-albert-donegan}

\bibitem{ErnestHall1934}
	\url{https://archive.org/details/ErnestHall1934}

\bibitem{WestAust1936}
	SOCIAL AND PERSONAL (1936, April 30). \emph{The West Australian} (Perth, WA: 1879--1954), p.~8.
	Retrieved April 7, 2020, from \url{http://nla.gov.au/nla.news-article25148694}

\bibitem{KingsParkDennisMartin}
	Honour Avenues plaques database, Flight Sergeant Dennis Martin.
	\url{https://www.bgpa.wa.gov.au/honour-avenues-plaques/1753-fsgt-dennis-martin}

\bibitem{WestAust1943}
	Advertising (1943, April 7). \emph{The West Australian} (Perth, WA : 1879--1954), p. 1.
	Retrieved April 11, 2020, from \url{http://nla.gov.au/nla.news-article46752091}

\bibitem{AWMJohnWalrond}
	Australian War Memorial catalogue entry.
	\url{https://www.awm.gov.au/collection/P10299621}

\bibitem{MartinWalmondEngagement}
	ENGAGEMENTS. (1940, July 22). \emph{The West Australian} (Perth, WA : 1879--1954), p. 10.
	Retrieved April 11, 2020, from \url{http://nla.gov.au/nla.news-article46727944}

\bibitem{MartinWalmondMarriage}
	Family Notices (1942, April 23). \emph{The West Australian} (Perth, WA : 1879--1954), p. 1.
	Retrieved April 11, 2020, from \url{http://nla.gov.au/nla.news-article47329581}

\bibitem{PatWalrondWesternMail}
	These people (1947, December 11). Western Mail (Perth, WA : 1885--1954), p. 33.
	Retrieved April 12, 2020, from \url{http://nla.gov.au/nla.news-article52177379}

\bibitem{WestAust1928}
	\emph{Family Notices} (1928, April 4). The West Australian, p. 1. \url{http://nla.gov.au/nla.news-article32102244}
	``AGNEW--WILSON.---On March 10, 1928, at the Ross Memorial Presbyterian Church, by the Rev. David Galloway,
	Robert Gordon, only son of Mr. and Mrs. R. Agnew, of Mt. Lawley,
	to Dorothy Jean, eldest daughter of Mr. and Mrs. J. H. Wilson, of Subiaco.''

\bibitem{BMD_WA_birth_1904}
	Western Australian BDM birth index entry, Fremantle 1904, no. 2724.

\bibitem{BMD_WA_birth_1904_Perth}
	Western Australian BDM birth index entry, Perth 1904, no. 5538.

\bibitem{BMD_WA_birth_1907}
	Western Australian Registry of Births, Marriages, and Deaths (birth in 1907). Beverley district, registration number 96.

\bibitem{BMD_WA_marriage_1929}
	Western Australian Registry of Births, Marriages, and Deaths (marriage in 1929). Perth district, registration number 1421.

\bibitem{BMD_WA_death_1953}
	Western Australian Registry of Births, Marriages, and Deaths (death in 1953). Gascoyne district, registration number 18.

\bibitem{Karrakatta_IA_208}
	Grave of Frederick Gordon Wilson, Karrakatta Cemetery, Presbyterian section IA, grave 208.

\end{thebibliography}
